### 2019-03-29 thesis_proposal_LaTeX/Chapters/1_Introduction.tex
share to GoogleDrive

Near-field electrospinning or NFES allows large scale manufacturability combined with controlled guidance. \cite{Madou2011} However, the reported efforts required the use of electric fields in excess of 200 kV/m for continuous operation so that the resulting in limited control for nano-fiber patterning. \cite{Madou2011} the current state-of-the-art synthesis processes for polymer nano-fibers lack to yield precise, inexpensive, fast, and continuous manufacturing properties.

>>>>

Near-field electrospinning or NFES allows large scale manufacturability combined with controlled guidance. \cite{Madou2011} However, the reported efforts required the use of electric fields in excess of 200 kV/m for continuous operation, resulting in limited control for nano-fiber patterning in traditional NFES processes. \cite{Madou2011} the current state-of-the-art synthesis processes for polymer nano-fibers lack to yield precise, inexpensive, fast, and continuous manufacturing properties.

### 2019-03-29 thesis_proposal_LaTeX/Chapters/3_HypothesisAndResearchQuestions.tex
share to GoogleDrive

@@

The rheological properties of polymer solutions along with synthesis parameters (stage velocity, voltage, dispense rate) can be amended to obtain a low voltage electrospun-able, photopolymerizable and graphitizable fibers to synthesize carbon nano-wires with specified dimensions (diameter and length).

>>>>

\subsubsection*{\color{mygray}[Chapter ready for review]}
% The system/technique/parameter X is better, for task Y, than each of its rivals Z, in dimension W.

@@

The rheological properties of polymer solutions along with synthesis parameters (stage velocity, voltage, dispense rate) can be amended to obtain a low voltage electrospun-able, photopolymerizable and graphitizable fibers for the synthesis of carbon nano-wires with specified dimensions (diameter and length).
